RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-26 manuscripts/manuscript.Rmd
typo fix

No data standard can anticipate all the uses and extensions researchers
may one day need. Researchers have repeatedly adapted the existing NEXUS
file format to accomidate encoding new kinds of information, but in the
process break compatibility between different flavors of NEXUS files, with
few reliable methods to distinguish between these flavors.  NeXML provides
a solution to this problem through the use of metadata annotation.

>>>>

No data standard can anticipate all the uses and extensions researchers
may one day need. Researchers have repeatedly adapted the existing NEXUS
file format to accommodate encoding new kinds of information, but in the
process break compatibility between different flavors of NEXUS files, with
few reliable methods to distinguish between these flavors.  NeXML provides
a solution to this problem through the use of metadata annotation.
